---
title: "Microbial biomass controls over the temperature sensitivity of soil respiration"
author: "Petr Capek, Robert Starke, Kirsten Hofmockel, Ben Bond-Lamberty, Nancy Hess"
date: "`r Sys.Date()`"
output:
  
  html_document: 
    theme: readable
    highlight: tango
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Data meta-analysis

To analyze data, several libraries have to uploaded. Then, data are uploaded (rsoil_tsensitivity_data11192018.csv). Data are available on https://github.com/petacapek/Rsoil_Tsensitivity.

```{r echo=FALSE, message=FALSE, warning=FALSE}
library(ggplot2)
library(dplyr)
library(gridExtra)
library(minpack.lm)
library(segmented)
library(arm)
library(FME)
library(DEoptim)
library(emmeans)
library(knitr)
library(kableExtra)
library(PerformanceAnalytics)

dat<-read.csv("rsoil_tsensitivity_data11192018.csv")
dat<-dat[order(dat$ID), ]
summary(dat)

```

First order decay equation and multiplicative equation are fitted across all observations. To fit the equations, Differential Evolution algorithm is used to minimize the objective function, which calculates Log Likelihood of the fit multiplied by negative 2. $R^{2}$ and AIC are calculated for each equation and compared.

```{r First order decay function, include=FALSE}
first_global<-function(data){
  
  #creating function for parameters estimation
  estim<-function(fr){
    #defining the objective function
    est<-function(x){
      
      parnames<-c("ks", "Eas")
      par<-x[1:length(parnames)]
      
      Ctot<-as.numeric(fr[, "Ctot"])
      Temp<-as.numeric(fr[, "Temperature"])
      
      yhat<-Ctot*par[1]*exp(par[2]/Temp/8.314)
      obs<-as.numeric(fr[, "Rsoil"])
      
      # SSres<-sum(((obs-yhat)^2), na.rm = T)
      # SStot<-sum(((obs-mean(obs, na.rm=T))^2), na.rm = T)
      # Rsq<-1-(SSres/SStot)
      ll<--length(obs)*log(2*mean(obs, na.rm=T)*sd(obs, na.rm=T)^2)/2-sum((obs-yhat)^2, na.rm=T)/2/sd(obs, na.rm=T)^2
      # AIC<-4-2*ll
      
      return(-2*ll)
      
    }
    
    #defining the goodness of fit function
    goodness<-function(x){
      
      parnames<-c("k", "Eas")
      par<-x[1:length(parnames)]
      
      Ctot<-as.numeric(fr[, "Ctot"])
      Temp<-as.numeric(fr[, "Temperature"])
      
      yhat<-Ctot*par[1]*exp(par[2]/Temp/8.314)
      obs<-as.numeric(fr[, "Rsoil"])
      
      SSres<-sum(((obs-yhat)^2), na.rm = T)
      SStot<-sum(((obs-mean(obs, na.rm=T))^2), na.rm = T)
      Rsq<-1-(SSres/SStot)
      ll<--length(obs)*log(2*mean(obs, na.rm=T)*sd(obs, na.rm=T)^2)/2-sum((obs-yhat)^2, na.rm=T)/2/sd(obs, na.rm=T)^2
      AIC<-4-2*ll
      
      return(c(R2=Rsq,AIC=AIC, ll=ll))
      
    }
    
    #approximate parameter estimation is done by MCMC method
    par_mcmc<-modMCMC(f=est, p=c(k=1e10, Eas=-50000),
                      lower=c(k=1e-6, Eas=-3000000),
                      upper=c(k=1e50, Eas=10000), niter=100000)
    
    #lower and upper limits for parameters are extracted
    pl<-summary(par_mcmc)["min",]
    pu<-summary(par_mcmc)["max",]
    
    #these limits are used to find global optimum by DEoptim
    opt_par<-DEoptim(fn=est, lower=pl, upper=pu,
                     control = c(itermax = 10000, steptol = 50, reltol = 1e-8,
                                 trace=FALSE, strategy=3, NP=500))
    
    #goodness of fit
    fit<-goodness(opt_par$optim$bestmem)
    
    #approximate parameter estimation is done by MCMC method
    par_prof<-modMCMC(f=est, p=opt_par$optim$bestmem,
                      lower=pl,
                      upper=pu, niter=100000)
    
    #goodness of fit
    fit<-goodness(opt_par$optim$bestmem)
    
    #best parameters
    p<-opt_par$optim$bestmem
    names(p)<-c("ks", "Eas")
    
    #sd of parameters
    p.sd<-summary(par_prof)[2,]
    
    #return list with opt_par and par_prof
    estim_out<-list()
    estim_out$pars<-p
    estim_out$pars.sd<-p.sd
    estim_out$fit<-fit
    
    return(estim_out)
  }
  
  #do the calculation
  res<-estim(fr=data)
  ks<-as.numeric(res$pars[1])
  Eas<-as.numeric(res$pars[2])
  ks.sd<-as.numeric(res$pars.sd[1])
  Eas.sd<-as.numeric(res$pars.sd[2])
  R2s<-as.numeric(res$fit[1])
  AICs<-as.numeric(res$fit[2])
  lls<-as.numeric(res$fit[3])
    
    
  
  return(c(ks=ks, Eas=Eas, ks.sd=ks.sd, Eas.sd=Eas.sd, R2=R2s, AIC=AICs, ll=lls))
  
}
```

```{r Multiplicative equation, include=FALSE}

coupled_global<-function(data){
  
  #creating function for parameters estimation
  estim<-function(fr){
    #defining the objective function
    est<-function(x){
      
      parnames<-c("ks", "Eas")
      par<-x[1:length(parnames)]
      
      Cmic<-as.numeric(fr[, "Biomass"])
      Ctot<-as.numeric(fr[, "Ctot"])
      Temp<-as.numeric(fr[, "Temperature"])
      
      yhat<-Ctot*Cmic*par[1]*exp(par[2]/Temp/8.314)
      obs<-as.numeric(fr[, "Rsoil"])
      
      # SSres<-sum(((obs-yhat)^2), na.rm = T)
      # SStot<-sum(((obs-mean(obs, na.rm=T))^2), na.rm = T)
      # Rsq<-1-(SSres/SStot)
      ll<--length(obs)*log(2*mean(obs, na.rm=T)*sd(obs, na.rm=T)^2)/2-sum((obs-yhat)^2, na.rm=T)/2/sd(obs, na.rm=T)^2
      # AIC<-4-2*ll
      
      return(-2*ll)
      
    }
    
    #defining the goodness of fit function
    goodness<-function(x){
      
      parnames<-c("k", "Eas")
      par<-x[1:length(parnames)]
      
      Cmic<-as.numeric(fr[, "Biomass"])
      Ctot<-as.numeric(fr[, "Ctot"])
      Temp<-as.numeric(fr[, "Temperature"])
      
      yhat<-Cmic*Ctot*par[1]*exp(par[2]/Temp/8.314)
      obs<-as.numeric(fr[, "Rsoil"])
      
      SSres<-sum(((obs-yhat)^2), na.rm = T)
      SStot<-sum(((obs-mean(obs, na.rm=T))^2), na.rm = T)
      Rsq<-1-(SSres/SStot)
      ll<--length(obs)*log(2*mean(obs, na.rm=T)*sd(obs, na.rm=T)^2)/2-sum((obs-yhat)^2, na.rm=T)/2/sd(obs, na.rm=T)^2
      AIC<-4-2*ll
      
      return(c(R2=Rsq,AIC=AIC, ll=ll))
      
    }
    
    #approximate parameter estimation is done by MCMC method
    par_mcmc<-modMCMC(f=est, p=c(k=1e10, Eas=-50000),
                      lower=c(k=1e-6, Eas=-3000000),
                      upper=c(k=1e50, Eas=10000), niter=100000)
    
    #lower and upper limits for parameters are extracted
    pl<-summary(par_mcmc)["min",]
    pu<-summary(par_mcmc)["max",]
    
    #these limits are used to find global optimum by DEoptim
    opt_par<-DEoptim(fn=est, lower=pl, upper=pu,
                     control = c(itermax = 10000, steptol = 50, reltol = 1e-8,
                                 trace=FALSE, strategy=3, NP=500))
    
    #goodness of fit
    fit<-goodness(opt_par$optim$bestmem)
    
    #approximate parameter estimation is done by MCMC method
    par_prof<-modMCMC(f=est, p=opt_par$optim$bestmem,
                      lower=pl,
                      upper=pu, niter=100000)
    
    #goodness of fit
    fit<-goodness(opt_par$optim$bestmem)
    
    #best parameters
    p<-opt_par$optim$bestmem
    names(p)<-c("ksb", "Easb")
    
    #sd of parameters
    p.sd<-summary(par_prof)[2,]
    
    #return list with opt_par and par_prof
    estim_out<-list()
    estim_out$pars<-p
    estim_out$pars.sd<-p.sd
    estim_out$fit<-fit
    
    return(estim_out)
  }
  
  #do the calculation
  res<-estim(fr=data)
  ksb<-as.numeric(res$pars[1])
  Easb<-as.numeric(res$pars[2])
  ksb.sd<-as.numeric(res$pars.sd[1])
  Easb.sd<-as.numeric(res$pars.sd[2])
  R2sb<-as.numeric(res$fit[1])
  AICsb<-as.numeric(res$fit[2])
  llsb<-as.numeric(res$fit[3])
    
    
  
  return(c(ksb=ksb, Easb=Easb, ksb.sd=ksb.sd, Easb.sd=Easb.sd, R2=R2sb, AIC=AICsb, ll=llsb))
  
}
```

```{r global comparison, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
first_order_global<-first_global(dat)
multi_global<-coupled_global(dat)

t.a1<-data.frame(Equation=c("First order decay", "Multiplicative"),
                 R2=c(first_order_global[5], multi_global[5]),
                 AIC=c(first_order_global[6], multi_global[6]),
                 dAIC=as.numeric(c(" ",first_order_global[6]-multi_global[6])),
                 p=c(" ", "<0.001"))

options(knitr.kable.NA = '')


kable(t.a1, digits = c(2), align = 'c', "html", booktabs=T, col.names = c('Equation', '$\\R^{2}$', 'AIC', '$\\Delta~AIC$', 'p'), caption = "_**Table S1:** Goodness of fit of the first order decay equation and the multiplicative equation with Arrhenius equation temperature response function. Goodness of fit is expressed as the coefficient of determination $R^2$ and Akaike Information Criterion (AIC). Equation fits are compared by AIC (see Mtareials and Methods for details.)_") %>% 
  kable_styling()

```

Results are further compared graphically. 

```{r Fig. 1 of the main text, echo=FALSE, fig.cap="Fig. S1: Goodness of correspondence between measured and predicted soil respiration rate. The respiration rate was predicted by two different equations (eq. 3 in the main text - First order and eq. 4 in the main text - Multiplicative equation, see Materials and Methods for details). Black dashed line represents 1:1 correspondence. Coefficient of determination (R2) is reported for each equation.  Both axis are on the logarithmic scale. ", fig.height=6, fig.width=12, message=FALSE, warning=FALSE}
ovp1<-dat[, c("Rsoil", "Biomass", "Ctot", "Temperature")]
ovp1$Legend<-c("First order")
ovp1$Pred<-ovp1$Ctot*first_order_global[1]*exp(first_order_global[2]/8.314/ovp1$Temperature)
lbfirst<-paste("R^2 == ", round(first_order_global[5], 2))

ovp2<-dat[, c("Rsoil", "Biomass", "Ctot", "Temperature")]
ovp2$Legend<-c("Multiplicative")
ovp2$Pred<-ovp2$Ctot*ovp2$Biomass*multi_global[1]*exp(multi_global[2]/8.314/ovp2$Temperature)
lbcoupled<-paste("R^2 == ", round(multi_global[5], 2))

ovp<-rbind(ovp1, ovp2)
ovp$Legend<-factor(ovp$Legend, levels=c("First order", "Multiplicative"))

#6 to 12 inches when exported to pdf
ggplot(ovp, aes(Rsoil, Pred))+geom_point(size=2,shape=21, alpha=0.5,fill="dodgerblue3")+
  geom_abline(intercept = 0, slope=1, lwd=0.5, colour="black", lty=2)+
  facet_grid(.~Legend)+
  scale_y_log10(limits=c(0.01,1000), breaks=c(0.01, 0.1, 1, 10, 100, 1000), 
                labels=c("0.01", "0.1", "1", "10", "100", "1000"))+
  scale_x_log10(limits=c(0.01,1000), breaks=c(0.01, 0.1, 1, 10, 100, 1000),
                labels=c("0.01", "0.1", "1", "10", "100", "1000"))+
  xlab(expression(paste("Measured respiration rate (nmol ",g^{-1}~h^{-1}, ")")))+
  ylab(expression(paste("Predicted respiration rate (nmol ",g^{-1}~h^{-1}, ")")))+
  geom_text(data=data.frame(x=0.03, y=900, label=c(lbfirst, lbcoupled), 
                            Legend=c("First order","Multiplicative")), 
            aes(x,y,label=label), inherit.aes=FALSE, parse=T, size=3.5)+
  theme_bw()+
  theme(axis.line.x = element_blank(),
        axis.line.y =element_blank(),
        plot.background=element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.text.y = element_text(size=10,colour="black"),
        axis.text.x = element_text(size=10,colour="black"),
        axis.title = element_text(size=10,colour="black"),
        legend.text=element_text(size=10,colour="black"),
        legend.title=element_blank(),
        legend.justification=c(1,0), legend.position=c(0.99,0.01),
        legend.key.size = unit(1,'lines'),
        legend.background=element_rect(fill=NA, colour=NA),
        strip.text.x = element_text(size=10),
        strip.background = element_rect(colour="black", fill = "white"),
        panel.spacing = unit(0.5, "lines"))
```

Next, presence of breakpoints in temperature response of heterotrophic soil respiration rate ($R_{SOIL}$) are analyzed for. The same analysis is conducted with scaled microbial biomass, expressed as log Response Ratio (see Materials and Methods in the main text for details). Results of the analysis are shown graphically. We use Arrhenius plot to vizualize the results.

```{r Fig. 2, echo=FALSE, warning=FALSE, fig.cap="Fig. S2: Arrhenius plot of the relationship between the temperature (inverted value multiplied by the gas constant, see eq. 6 in Materials and Methods for details) and the natural logarithm of soil respiration rate (blue points, left y-axis). Symbols represent median respiration rate calculated over five degrees Kelvin interval increments (the whole temperature range is 274.6 - 323.1 K, i.e. 2 - 50°C). Error bars represent upper and lower quartiles. Vertical dashed line represent breakpoint temperature (25.2 ± 2.4 °C) at which the temperature sensitivity of soil respiration rate changes. Blue dashed line represents segmented linear regression (eq. 6). The breakpoint temperature corresponds with the breakpoint temperature of decadic logarithm of soil microbial biomass response ratio ($logRR_{Biomass}$, grey points, right y-axis). $logRR_{Biomass}$ defines the magnitude of change of microbial biomass at the given temperature relative to control. Control is defined as the microbial biomass at the the temperature 15°C or the closest temperature within a respective data set. $logRR_{Biomass}$ zero (solid horizontal line) indicates no change of microbial biomass relative to control. $logRR_{Biomass}$ less than zero indicates decrease of microbial biomass relative to control and vice versa.  Symbols represent median $logRR_{Biomass}$ calculated over five degrees Kelvin interval increments. Error bars represent upper and lower quartiles."}
rbg<-dat
rbg$Temp<-1/8.314/(rbg$Temperature)
rbg$Tcut<-cut(rbg$Temperature, 20)

#calculate median and quartiles for respiration rate and biomass
rbg_sum<-rbg %>% group_by(Tcut) %>% summarize(Rmed=log(median(Rsoil, na.rm=T)),
                                              Rl=log(quantile(Rsoil, probs = 0.25, na.rm = T)),
                                              Ru=log(quantile(Rsoil, probs = 0.75, na.rm = T)),
                                              Bmed=log10(median(Bscaled, na.rm=T)),
                                              Bl=log10(quantile(Bscaled, probs = 0.25, na.rm = T)),
                                              Bu=log10(quantile(Bscaled, probs = 0.75, na.rm = T)),
                                              Temp=median(Temp))

#statistic
lm.all<-lm(log(Rsoil)~Temp, offset = log(Ctot), rbg)
all.o<-segmented(lm.all, seg.Z = ~Temp)
break.all<-all.o$psi[2]
1/break.all/8.314-273.15
#davies.test(lm.all, ~Temp)
Predictions<-data.frame(Temp=1/8.314/seq(273.15, 323.15))
Predictions$all<-predict(all.o, newdata=Predictions)

#biomass scaled
lmb.all<-lm(log(Bscaled)~Temp, rbg)
lmb.o<-segmented(lmb.all, seg.Z = ~Temp)
#summary(lmb.o)
break.b<-lmb.o$psi[2]
1/break.b/8.314-273.15
#davies.test(lmb.all, ~Temp)


#6 to 8 inches when exported to pdf
ggplot(rbg_sum, aes(x=Temp))+
  geom_hline(yintercept = 0)+
  geom_vline(xintercept = break.all, lwd=0.5, colour="black", lty=2)+
  geom_errorbar(aes(ymin=Rl, ymax=Ru),colour="black",width=0.000001)+
  geom_point(size=2,shape=21, aes(y=Rmed, fill="Respiration rate"))+
  geom_line(data = Predictions, aes(x=Temp, y=all*1.137391),colour="dodgerblue3", lwd=0.5, lty=2)+
  geom_errorbar(aes(ymin=Bl*5, ymax=Bu*6),colour="black",width=0.000001)+
  geom_point(size=2,shape=21, aes(y=Bmed*5, fill="Biomass"))+
  scale_y_continuous(sec.axis = sec_axis(~./5, 
                                         name = expression(paste(italic("log")~RR[Biomass]))))+
  scale_colour_manual(values = c("grey60", "dodgerblue3"))+
  scale_fill_manual(values = c("grey60", "dodgerblue3"))+
  labs(y = expression(paste(italic("ln") ,"(Respiration rate) (nmol ",g^{-1}~h^{-1}, ")")),
       x = expression(paste(frac(1,8.314%*%Temperature~(K)))),
       colour = "Legend")+
  theme_bw()+
  theme(axis.line.x = element_blank(),
        axis.line.y =element_blank(),
        plot.background=element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.text.y = element_text(size=10,colour="black"),
        axis.text.x = element_text(size=10,colour="black"),
        axis.title = element_text(size=10,colour="black"),
        legend.text=element_text(size=10,colour="black"),
        legend.title=element_blank(),
        legend.justification=c(1,0), legend.position=c(0.99,0.01),
        legend.key.size = unit(1,'lines'),
        legend.background=element_rect(fill=NA, colour=NA),
        strip.text.x = element_text(size=10),
        strip.background = element_rect(colour="black", fill = "white"),
        panel.spacing = unit(0.25, "lines"))
```

As shown above, there is one significant breakpoint in the relationship between the temperature and $R_{SOIL}$ at the temperature 25.3°C. There is also one significant breakpoint in the relationship between the temperature and microbial biomass log Response ratio ($logRR_{Biomass}$ in Fig. 2) at the temperature 27.1°C. Given the standard error of the estimate (2.4°C and 1°C), both estimates are statistically same.

The same analysis is conducted with four different soils published by Santruckova et al. (2003). Results of the analysis are shown graphically. 

```{r Fig. 3, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Fig. S3: Respiration rate (blue points, left y-axis) and the microbial biomass (grey points, right y-axis) as a function of the temperature in four different soils (Santruckova et al., 2003). Blue solid lines represent segmented linear regression (eq. 6). Coefficient of determination of the regression is reported (R2). Vertical black dashed lines represent the breakpoint temperature of segmented linear regression. Blue dot-dashed line represent the best fit of Macromolecular Rate Theory equation (eq. 8). For all soils, the segmented linear regression fits the data significantly better than Macromolecular Rate Theory equation (???AIC = -45.3, p<0.001 for Pokulikha; ???AIC = -6.6, p=0.037 for Zotino; ???AIC = -74.6, p<0.001 for Bakhta; ???AIC = -64.1, p<0.001 for Nazimovo). Note that each box have different scale of left and right y-axis."}

dat$Temp<-1/dat$Temperature/8.314

#31
###statistics
lm31<-lm(log(Rsoil)~Temp, subset(dat, ID==31))
o31<-segmented(lm31, seg.Z = ~Temp)
break31<-o31$psi[2]
Predictions$o31<-predict(o31, newdata=Predictions)
lb31<-paste("R^2 == ", round(as.numeric(summary(o31)[8]), 2))

# lm31b<-lm(log(Biomass)~Temp, subset(dat, ID==31))
# b31<-segmented(lm31b, seg.Z = ~Temp)
1/8.314/o31$psi[2]-273.15
(1/8.314/o31$psi[2]-273.15)-(1/8.314/(o31$psi[2]+o31$psi[3])-273.15)

###MMR
mmr<-function(data){
  cost<-function(x){
    par<-(x)
    names(par)<-c("dH", "dCp", "dS", "Topt")
    
    obs<-log(data[,"Rsoil"])
    Temp<-data[,"Temperature"]
    Ctot<-log(data[,"Ctot"])
    
    
    yhat<-Ctot+log(1.38e-23*Temp/6.63e-34*3600)-(par[1]+par[2]*(Temp-par[4]))/8.314/Temp+
      (par[3]+par[2]*(log(Temp)-log(par[4])))/8.314
    
    ll<--length(obs)*log(2*mean(obs, na.rm=T)*sd(obs, na.rm=T)^2)/2-sum((obs-yhat)^2, na.rm=T)/2/sd(obs, na.rm=T)^2
    
    return(-2*ll)
  }
  
  #approximate parameter estimation is done by MCMC method
  par_mcmc<-modMCMC(f=cost, p=c(dH=10000, dCp=-3000, dS=5000, Topt=300),
                    lower=c(dH=-100000, dCp=-300000, dS=-50000, Topt=273.15),
                    upper=c(dH=100000, dCp=300000, dS=50000, Topt=350), niter=50000)
  
  #lower and upper limits for parameters are extracted
  pl<-summary(par_mcmc)["min",]
  pu<-summary(par_mcmc)["max",]
  
  #these limits are used to find global optimum by DEoptim
  opt_par<-DEoptim(fn=cost, lower=pl, upper=pu,
                   control = c(itermax = 10000, steptol = 50, reltol = 1e-8,
                               trace=FALSE, strategy=3, NP=250))
  return(opt_par$optim$bestmem)
}

mmr31<-mmr(dat[dat$ID==31, ])



dat31<-subset(dat, ID==31)
dat31$label<-c("Pokulikha")

fig31<-ggplot(dat31, aes(x=Temperature-273.15))+
    geom_point(size=2,shape=21, alpha=0.5, aes(y=Rsoil, fill="Respiration rate"))+
    geom_line(aes(y=exp(log(Ctot)+log(1.38e-23*Temperature/6.63e-34*3600)-(mmr31[1]+mmr31[2]*(Temperature-mmr31[4]))/8.314/Temperature+
                          (mmr31[3]+mmr31[2]*(log(Temperature)-log(mmr31[4])))/8.314)),
              lwd=0.5,colour="dodgerblue3", lty=4)+
    geom_line(data=Predictions, aes(x=1/8.314/Temp-273.15, y=exp(o31)),colour="dodgerblue3", lwd=0.5)+
    geom_point(size=2,shape=21, alpha=0.5, aes(y=Biomass*1.1, fill="Biomass"))+
    scale_y_continuous(sec.axis = sec_axis(~./1.1, 
                       name = c(" ")))+
    scale_colour_manual(values = c("grey60", "dodgerblue3"))+
    scale_fill_manual(values = c("grey60", "dodgerblue3"))+
    geom_vline(xintercept = 1/8.314/break31-273.15, lwd=0.5, colour="black", lty=2)+
    xlim(5,42)+
    labs(y = expression(paste("Respiration rate (nmol ",g^{-1}~h^{-1}, ")")),
         x = "Temperature (°C)",
         colour = "Legend")+
    annotate("text", x=9, y=60, label=lb31, parse=T, size=3.5)+
    theme_bw()+
    theme(axis.line.x = element_blank(),
          axis.line.y =element_blank(),
          plot.background=element_blank(),
          axis.title.x = element_blank(),
          axis.ticks.x = element_blank(),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          axis.text.x = element_blank(),
          axis.text = element_text(size=10,colour="black"),
          legend.text=element_text(size=10,colour="black"),
          legend.title=element_blank(),
          legend.justification=c(0,1), legend.position=c(0.01,0.99),
          legend.key.size = unit(1,'lines'),
          legend.background=element_rect(fill=NA, colour=NA),
          strip.text.x = element_text(size=10),
          strip.background = element_rect(colour="black", fill = "white"),
          plot.margin = unit(c(0.1, 0.08, 0,0.1), "in"))+facet_wrap(~label)

#32
###statistics
lm32<-lm(log(Rsoil)~Temp, subset(dat, ID==32))
o32<-segmented(lm32, seg.Z = ~Temp)
break32<-o32$psi[2]
Predictions$o32<-predict(o32, newdata=Predictions)
lb32<-paste("R^2 == ", round(as.numeric(summary(o32)[8]), 2))

mmr32<-mmr(dat[dat$ID==32, ])

# lm32b<-lm(log(Biomass)~Temp, subset(dat.results2, ID==32))
# b32<-segmented(lm32b, seg.Z = ~Temp)
1/8.314/o32$psi[2]-273.15
(1/8.314/o32$psi[2]-273.15)-(1/8.314/(o32$psi[2]+o32$psi[3])-273.15)

dat32<-subset(dat, ID==32)
dat32$label<-c("Bakhta")

fig32<-ggplot(dat32, aes(x=Temperature-273.15))+
    geom_point(size=2,shape=21, alpha=0.5, aes(y=Rsoil, fill="Respiration rate"))+
    geom_line(aes(y=exp(log(Ctot)+log(1.38e-23*Temperature/6.63e-34*3600)-(mmr32[1]+mmr32[2]*(Temperature-mmr32[4]))/8.314/Temperature+
                          (mmr32[3]+mmr32[2]*(log(Temperature)-log(mmr32[4])))/8.314)),
              lwd=0.5,colour="dodgerblue3", lty=4)+
    geom_line(data=Predictions, aes(x=1/8.314/Temp-273.15, y=exp(o32)), colour="dodgerblue3", lwd=0.5)+
    geom_point(size=2,shape=21, alpha=0.5, aes(y=Biomass*1.1, fill="Biomass"))+
    scale_y_continuous(sec.axis = sec_axis(~./1.1, 
                       name = c(" ")))+
    scale_colour_manual(values = c("grey60", "dodgerblue3"))+
    scale_fill_manual(values = c("grey60", "dodgerblue3"))+
    geom_vline(xintercept = 1/8.314/break32-273.15, lwd=0.5, colour="black", lty=2)+
    xlim(5,42)+
    labs(y = expression(paste("Respiration rate (nmol ",g^{-1}~h^{-1}, ")")),
         x = "Temperature (°C)",
         colour = "Legend")+
    annotate("text", x=9, y=155, label=lb32, parse=T, size=3.5)+
    theme_bw()+
    theme(axis.line.x = element_blank(),
          axis.line.y =element_blank(),
          plot.background=element_blank(),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          axis.text = element_text(size=10,colour="black"),
          legend.text=element_text(size=10,colour="black"),
          legend.title=element_blank(),
          legend.justification=c(0,1), legend.position="none",
          legend.key.size = unit(1,'lines'),
          legend.background=element_rect(fill=NA, colour=NA),
          strip.text.x = element_text(size=10),
          strip.background = element_rect(colour="black", fill = "white"),
          plot.margin = unit(c(0, 0, 0.1,0.1), "in"))+facet_wrap(~label)

#33
###statistics
lm33<-lm(log(Rsoil)~Temp, subset(dat, ID==33))
o33<-segmented(lm33, seg.Z = ~Temp)
break33<-o33$psi[2]
Predictions$o33<-predict(o33, newdata=Predictions)
lb33<-paste("R^2 == ", round(as.numeric(summary(o33)[8]), 2))

mmr33<-mmr(dat[dat$ID==33, ])

# lm33b<-lm(log(Biomass)~Temp, subset(dat.results2, ID==33))
# b33<-segmented(lm33b, seg.Z = ~Temp)
1/8.314/o33$psi[2]-273.15
(1/8.314/o33$psi[2]-273.15)-(1/8.314/(o33$psi[2]+o33$psi[3])-273.15)

dat33<-subset(dat, ID==33)
dat33$label<-c("Zotino")

fig33<-ggplot(dat33, aes(x=Temperature-273.15))+
    geom_point(size=2,shape=21, alpha=0.5, aes(y=Rsoil, fill="Respiration rate"))+
    geom_line(aes(y=exp(log(Ctot)+log(1.38e-23*Temperature/6.63e-34*3600)-(mmr33[1]+mmr33[2]*(Temperature-mmr33[4]))/8.314/Temperature+
                          (mmr33[3]+mmr33[2]*(log(Temperature)-log(mmr33[4])))/8.314)),
              lwd=0.5,colour="dodgerblue3", lty=4)+
    geom_line(data=Predictions, aes(x=1/8.314/Temp-273.15, y=exp(o33)), colour="dodgerblue3", lwd=0.5)+
    geom_point(size=2,shape=21, alpha=0.5, aes(y=Biomass/5, fill="Biomass"))+
    scale_y_continuous(sec.axis = sec_axis(~.*5, 
                       name = expression(paste("Biomass (", mu, "mol ",g^{-1}, ")"))))+
    scale_colour_manual(values = c("grey60", "dodgerblue3"))+
    scale_fill_manual(values = c("grey60", "dodgerblue3"))+
    geom_vline(xintercept = 1/8.314/break33-273.15, lwd=0.5, colour="black", lty=2)+
    xlim(5,42)+
    labs(y = (" "),
         x = "Temperature (°C)",
         colour = "Legend")+
    annotate("text", x=9, y=15.5, label=lb33, parse=T, size=3.5)+
    theme_bw()+
    theme(axis.line.x = element_blank(),
          axis.line.y =element_blank(),
          axis.title.x = element_blank(),
          plot.background=element_blank(),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          axis.ticks.x = element_blank(),
          axis.text.x = element_blank(),
          axis.text = element_text(size=10,colour="black"),
          legend.text=element_text(size=10,colour="black"),
          legend.title=element_blank(),
          legend.justification=c(0,1), legend.position="none",
          legend.key.size = unit(1,'lines'),
          legend.background=element_rect(fill=NA, colour=NA),
          strip.text.x = element_text(size=10),
          strip.background = element_rect(colour="black", fill = "white"),
          plot.margin = unit(c(0.1, 0.18, 0,0), "in"))+facet_wrap(~label)

#34
###statistics
lm34<-lm(log(Rsoil)~Temp, subset(dat, ID==34))
o34<-segmented(lm34, seg.Z = ~Temp)
break34<-o34$psi[2]
Predictions$o34<-predict(o34, newdata=Predictions)
lb34<-paste("R^2 == ", round(as.numeric(summary(o34)[8]), 2))

mmr34<-mmr(dat[dat$ID==34, ])

# lm34b<-lm(log(Biomass)~Temp, subset(dat.results2, ID==34))
# b34<-segmented(lm34b, seg.Z = ~Temp)
1/8.314/o34$psi[2]-273.15
(1/8.314/o34$psi[2]-273.15)-(1/8.314/(o34$psi[2]+o34$psi[3])-273.15)

dat34<-subset(dat, ID==34)
dat34$label<-c("Nazimovo")



fig34<-ggplot(dat34, aes(x=Temperature-273.15))+
    geom_point(size=2,shape=21, alpha=0.5, aes(y=Rsoil, fill="Respiration rate"))+
    geom_line(aes(y=exp(log(Ctot)+log(1.38e-23*Temperature/6.63e-34*3600)-(mmr34[1]+mmr34[2]*(Temperature-mmr34[4]))/8.314/Temperature+
                          (mmr34[3]+mmr34[2]*(log(Temperature)-log(mmr34[4])))/8.314)),
              lwd=0.5,colour="dodgerblue3", lty=4)+
    geom_line(data=Predictions, aes(x=1/8.314/Temp-273.15, y=exp(o34)), colour="dodgerblue3", lwd=0.5)+
    geom_point(size=2,shape=21, alpha=0.5, aes(y=Biomass/5, fill="Biomass"))+
    scale_y_continuous(sec.axis = sec_axis(~.*5, 
                                           name = expression(paste("Biomass (", mu, "mol ",g^{-1}, ")"))))+
    scale_colour_manual(values = c("grey60", "dodgerblue3"))+
    scale_fill_manual(values = c("grey60", "dodgerblue3"))+
    geom_vline(xintercept = 1/8.314/break34-273.15, lwd=0.5, colour="black", lty=2)+
    xlim(5,42)+
    labs(y = (" "),
         x = "Temperature (°C)",
         colour = "Legend")+
    annotate("text", x=20, y=41, label=lb34, parse=T, size=3.5)+
    theme_bw()+
    theme(axis.line.x = element_blank(),
          axis.line.y =element_blank(),
          plot.background=element_blank(),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          axis.text = element_text(size=10,colour="black"),
          legend.text=element_text(size=10,colour="black"),
          legend.title=element_blank(),
          legend.justification=c(0,1), legend.position="none",
          legend.key.size = unit(1,'lines'),
          legend.background=element_rect(fill=NA, colour=NA),
          strip.text.x = element_text(size=10),
          strip.background = element_rect(colour="black", fill = "white"),
          plot.margin = unit(c(0, 0.1, 0.1,0), "in"))+facet_wrap(~label)

#6 to 8 inches when exported to pdf
grid.arrange(fig31, fig33, fig32, fig34, ncol=2)
```

In fig. S3, temperature response of $R_{SOIL}$ is fitted by the first order decay equation with Arrhenius equation as a tempeture response function and with two temperature sensitivities for two temperature intervals (soild line in fig. S3). Alternatively, Macromolecular Rate Theory equation (see Materials and Methods for details) can be used. This equation was used previously to explain attenuation of temperature sensitivity of $R_{SOIL}$ (dot-dashed line in fig. S3). Fit of both equations are compared by AIC

```{r echo=TRUE, message=FALSE, warning=FALSE, results='asis'}

#31
AICcalc<-function(Observed, Predicted, ncoef){
  ll<--length(Observed)*log(2*mean(Observed, na.rm=T)*sd(Observed, na.rm=T)^2)/2-sum((Observed-Predicted)^2, na.rm=T)/2/sd(Observed, na.rm=T)^2
  return(2*ncoef-2*ll)
}

#segmented
AIC31<-AICcalc(Observed=dat[(!is.na(dat$Rsoil) & dat$ID==31), "Rsoil"],
        Predicted = exp(predict(o31)), ncoef = 3)
#mmr
MMR31<-AICcalc(Observed=dat[(!is.na(dat$Rsoil) & dat$ID==31), "Rsoil"],
        Predicted = with(dat[(!is.na(dat$Rsoil) & dat$ID==31),],
                         exp(log(Ctot)+log(1.38e-23*Temperature/6.63e-34*3600)-(mmr31[1]+mmr31[2]*(Temperature-mmr31[4]))/8.314/Temperature+
                               (mmr31[3]+mmr31[2]*(log(Temperature)-log(mmr31[4])))/8.314)), ncoef = 4)

exp((AIC31-MMR31)/2)

#32
#segmented
AIC32<-AICcalc(Observed=dat[(!is.na(dat$Rsoil) & dat$ID==32), "Rsoil"],
        Predicted = exp(predict(o32)), ncoef = 3)
#mmr
MMR32<-AICcalc(Observed=dat[(!is.na(dat$Rsoil) & dat$ID==32), "Rsoil"],
        Predicted = with(dat[(!is.na(dat$Rsoil) & dat$ID==32),],
                         exp(log(Ctot)+log(1.38e-23*Temperature/6.63e-34*3600)-(mmr32[1]+mmr32[2]*(Temperature-mmr32[4]))/8.314/Temperature+
                               (mmr32[3]+mmr32[2]*(log(Temperature)-log(mmr32[4])))/8.314)), ncoef = 4)

exp((AIC32-MMR32)/2)

#33
#segmented
AIC33<-AICcalc(Observed=dat[(!is.na(dat$Rsoil) & dat$ID==33), "Rsoil"],
        Predicted = exp(predict(o33)), ncoef = 3)
#mmr
MMR33<-AICcalc(Observed=dat[(!is.na(dat$Rsoil) & dat$ID==33), "Rsoil"],
        Predicted = with(dat[(!is.na(dat$Rsoil) & dat$ID==33),],
                         exp(log(Ctot)+log(1.38e-23*Temperature/6.63e-34*3600)-(mmr33[1]+mmr33[2]*(Temperature-mmr33[4]))/8.314/Temperature+
                               (mmr33[3]+mmr33[2]*(log(Temperature)-log(mmr33[4])))/8.314)), ncoef = 4)

exp((AIC33-MMR33)/2)


#34

#segmented
AIC34<-AICcalc(Observed=dat[(!is.na(dat$Rsoil) & dat$ID==34), "Rsoil"],
        Predicted = exp(predict(o34)), ncoef = 3)
#mmr
MMR34<-AICcalc(Observed=dat[(!is.na(dat$Rsoil) & dat$ID==34), "Rsoil"],
        Predicted = with(dat[(!is.na(dat$Rsoil) & dat$ID==34),],
                         exp(log(Ctot)+log(1.38e-23*Temperature/6.63e-34*3600)-(mmr34[1]+mmr34[2]*(Temperature-mmr34[4]))/8.314/Temperature+
                               (mmr34[3]+mmr34[2]*(log(Temperature)-log(mmr34[4])))/8.314)), ncoef = 4)

exp((AIC34-MMR34)/2)

t.a2<-data.frame(AIC=c(AIC31, MMR31, AIC32, MMR32, AIC33, MMR33, AIC34, MMR34),
                 dAIC=c(NA, AIC31-MMR31, NA, AIC32-MMR32, NA, AIC33-MMR33,NA, AIC34-MMR34),
                 p=c(NA, exp((AIC31-MMR31)/2), NA, exp((AIC32-MMR32)/2), NA, exp((AIC33-MMR33)/2), NA, exp((AIC34-MMR34)/2)))

options(knitr.kable.NA = '')


kable(t.a2, digits = c(2), align = 'c', "html", booktabs=T, col.names = c('AIC', '$\\Delta~AIC$', 'p'), row.names=F, caption = "Table S2: Goodness of fit of two equations (first order decay equation with Arrhenius equation as a tempeture response function and with two temperature sensitivities for two temperature intervals, and Macromolecular Rate theory equation respectively) calculated for four different soils shown in Fig. S3. Goodness of fit is expressed as Akaike Infromation Criterion (AIC). Difference in AIC ($\Delta~AIC$) of two equations and its statistical significance (p) is reported.") %>% 
  kable_styling(bootstrap_options = c("hover")) %>%
  group_rows("Pokulikha", 1, 2) %>%
  group_rows("Bakhta", 3, 4) %>%
  group_rows("Zotino", 5, 6) %>%
  group_rows("Nazimovo", 7, 8)



```


To evaluate the effect of temperature-associated changes of microbial biomass on apparent temperature sensitivity of $R_{SOIL}$, activation energy parameter ($E_{A}$) of the Arrhenius equation is estimated for each observation separately. This is done for the first order decay equation and multiplicative equation.

```{r par estimates 1, message=FALSE, warning=FALSE, include=FALSE}

first_order<-function(data){
  
  #list of unique observations
  IDs<-unique(data$ID)
  
  #defining all variables to calculate
  #parameters
  logks<-numeric()
  Eas<-numeric()
  
  #standard errors
  logks.sd<-numeric()
  Eas.sd<-numeric()
  
  #r.squared
  R2s<-numeric()
  
  #AIC
  AICs<-numeric()
  
  #Log likelihood
  lls<-numeric()
  
  #creating function for parameters estimation
  estim<-function(fr){
    
    #defining the goodness of fit function
    goodness<-function(x){
      
      Ctot<-as.numeric(fr[, "Ctot"])
      Temp<-as.numeric(fr[, "Temperature"])
      
      yhat<-Ctot*exp(x[1])*exp(x[2]/Temp/8.314)
      obs<-as.numeric(fr[, "Rsoil"])
      
      SSres<-sum(((obs-yhat)^2), na.rm = T)
      SStot<-sum(((obs-mean(obs, na.rm=T))^2), na.rm = T)
      Rsq<-1-(SSres/SStot)
      ll<--length(obs)*log(2*mean(obs, na.rm=T)*sd(obs, na.rm=T)^2)/2-sum((obs-yhat)^2, na.rm=T)/2/sd(obs, na.rm=T)^2
      AIC<-4-2*ll
      
      return(c(R2=Rsq,AIC=AIC, ll=ll))
      
    }
    
    #estimation is done by linear regression
    Ctot<-log(as.numeric(fr[, "Ctot"]))
    Temp<-1/8.314/as.numeric(fr[, "Temperature"])
    obs<-log(as.numeric(fr[, "Rsoil"]))
    
    lmf<-lm(obs~Temp, offset = Ctot)
    blmf<-sim(lmf, n.sim=10000)  
    
    #goodness of fit
    fit<-goodness(coef(lmf))
    
    #best parameters
    p<-coef(lmf)
    names(p)<-c("logks", "Eas")
    
    #sd of parameters
    p.sd<-apply(coef(blmf), 2, sd)
    
    #return list with opt_par and par_prof
    estim_out<-list()
    estim_out$pars<-p
    estim_out$pars.sd<-p.sd
    estim_out$fit<-fit
    
    return(estim_out)
  }
  
  #do the calculation
  for(i in IDs){
    
    res<-estim(fr=data[data$ID==i, ])
    
    logks<-append(logks, rep(as.numeric(res$pars[1]), times=nrow(data[data$ID==i, ])))
    Eas<-append(Eas, rep(as.numeric(res$pars[2]), times=nrow(data[data$ID==i, ])))
    logks.sd<-append(logks.sd, rep(as.numeric(res$pars.sd[1]), times=nrow(data[data$ID==i, ])))
    Eas.sd<-append(Eas.sd, rep(as.numeric(res$pars.sd[2]), times=nrow(data[data$ID==i, ])))
    R2s<-append(R2s, rep(as.numeric(res$fit[1]), times=nrow(data[data$ID==i, ])))
    AICs<-append(AICs, rep(as.numeric(res$fit[2]), times=nrow(data[data$ID==i, ])))
    lls<-append(lls, rep(as.numeric(res$fit[3]), times=nrow(data[data$ID==i, ])))
    
    }
  
  return(data.frame(logks, Eas, logks.sd, Eas.sd, R2s, AICs, lls))
  
}

dat.results<-cbind(dat, first_order(dat))

```

```{r par estimates 2, message=FALSE, warning=FALSE, include=FALSE}
coupled<-function(data){
  
  #list of unique observations
  IDs<-unique(data$ID)
  
  #defining all variables to calculate
  #parameters
  logksb<-numeric()
  Easb<-numeric()
  
  #standard errors
  logksb.sd<-numeric()
  Easb.sd<-numeric()
  
  #r.squared
  R2sb<-numeric()
  
  #AIC
  AICsb<-numeric()
  
  #Log likelihood
  llsb<-numeric()
  
  #creating function for parameters estimation
  estim<-function(fr){
    
    #defining the goodness of fit function
    goodness<-function(x){
      
      Ctot<-as.numeric(fr[, "Ctot"])
      Cmic<-as.numeric(fr[, "Biomass"])
      Temp<-as.numeric(fr[, "Temperature"])
      
      yhat<-Ctot*Cmic*exp(x[1])*exp(x[2]/Temp/8.314)
      obs<-as.numeric(fr[, "Rsoil"])
      
      SSres<-sum(((obs-yhat)^2), na.rm = T)
      SStot<-sum(((obs-mean(obs, na.rm=T))^2), na.rm = T)
      Rsq<-1-(SSres/SStot)
      ll<--length(obs)*log(2*mean(obs, na.rm=T)*sd(obs, na.rm=T)^2)/2-sum((obs-yhat)^2, na.rm=T)/2/sd(obs, na.rm=T)^2
      AIC<-4-2*ll
      
      return(c(R2=Rsq,AIC=AIC, ll=ll))
      
    }
    
    #estimation is done by linear regression
    Ctot<-log(as.numeric(fr[, "Ctot"]))
    Cmic<-log(as.numeric(fr[, "Biomass"]))
    Temp<-1/8.314/as.numeric(fr[, "Temperature"])
    obs<-log(as.numeric(fr[, "Rsoil"]))
    
    lmf<-lm(obs~Temp, offset = Ctot+Cmic)
    blmf<-sim(lmf, n.sim=10000)  
    
    #goodness of fit
    fit<-goodness(coef(lmf))
    
    #best parameters
    p<-coef(lmf)
    names(p)<-c("logks", "Eas")
    
    #sd of parameters
    p.sd<-apply(coef(blmf), 2, sd)
    
    #return list with opt_par and par_prof
    estim_out<-list()
    estim_out$pars<-p
    estim_out$pars.sd<-p.sd
    estim_out$fit<-fit
    
    return(estim_out)
  }
  
  #do the calculation
  for(i in IDs){
    
    res<-estim(fr=data[data$ID==i, ])
    
    logksb<-append(logksb, rep(as.numeric(res$pars[1]), times=nrow(data[data$ID==i, ])))
    Easb<-append(Easb, rep(as.numeric(res$pars[2]), times=nrow(data[data$ID==i, ])))
    logksb.sd<-append(logksb.sd, rep(as.numeric(res$pars.sd[1]), times=nrow(data[data$ID==i, ])))
    Easb.sd<-append(Easb.sd, rep(as.numeric(res$pars.sd[2]), times=nrow(data[data$ID==i, ])))
    R2sb<-append(R2sb, rep(as.numeric(res$fit[1]), times=nrow(data[data$ID==i, ])))
    AICsb<-append(AICsb, rep(as.numeric(res$fit[2]), times=nrow(data[data$ID==i, ])))
    llsb<-append(llsb, rep(as.numeric(res$fit[3]), times=nrow(data[data$ID==i, ])))
    
  }
  
  return(data.frame(logksb, Easb, logksb.sd, Easb.sd, R2sb, AICsb, llsb))
  
}

dat.results<-cbind(dat.results, coupled(dat))

```

All data are visualized.

```{r fig.height=35, fig.width=10, message=FALSE, warning=FALSE, fig.cap="Fig. S4: Correspondence between the measured respiration rates (blue points) and the respiration rates predicted by two equations (eq. 3 - solid line, eq. 4 - dashed, see Materials and Methods section for details). One panel corresponds to one observation."}

ggplot(dat.results, aes(Temperature-273.15, Rsoil))+
  geom_point(size=2,shape=21, alpha=0.5, fill="dodgerblue3", show.legend=F)+
  geom_line(aes(Temperature-273.15,Ctot*exp(logks)*exp(Eas/Temperature/8.314)), 
            show.legend=F)+
  geom_line(aes(Temperature-273.15,Ctot*Biomass*exp(logksb)*exp(Easb/Temperature/8.314)), 
           show.legend=F, lty=2)+
  facet_wrap(~ID, scales="free", ncol = 6)+xlab("Temperature (°C)")+
  ylab(expression(paste("Respiration rate (nmol ",g^{-1}~h^{-1}, ")")))+theme_bw()+
  theme(axis.line.x = element_blank(),
        axis.line.y =element_blank(),
        plot.background=element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.text.y = element_text(size=10,colour="black"),
        axis.text.x = element_text(size=10,colour="black"),
        axis.title = element_text(size=10,colour="black"),
        legend.text=element_text(size=10,colour="black"),
        legend.title=element_blank(),
        legend.justification=c(1,0), legend.position=c(0.99,0.01),
        legend.key.size = unit(1,'lines'),
        legend.background=element_rect(fill=NA, colour=NA),
        strip.text.x = element_text(size=10),
        strip.background = element_rect(colour="black", fill = "white"),
        panel.spacing = unit(0.5, "lines"))
```

$E_{A}$ estimates are summarized in following table.

```{r echo=TRUE, message=FALSE, warning=FALSE, results='asis'}

res<-subset(dat.results, !duplicated(Eas))

t.a3<-data.frame(Minimum=c(summary(res$Eas)[1]/1000, summary(res$Easb)[1]/1000),
                 ql=c(summary(res$Eas)[2]/1000, summary(res$Easb)[2]/1000),
                 Median=c(summary(res$Eas)[3]/1000, summary(res$Easb)[3]/1000),
                 Mean=c(summary(res$Eas)[4]/1000, summary(res$Easb)[4]/1000),
                 qu=c(summary(res$Eas)[5]/1000, summary(res$Easb)[5]/1000),
                 Maximum=c(summary(res$Eas)[6]/1000, summary(res$Easb)[6]/1000))

rownames(t.a3)<-c("First order decay", "Multiplicative")


kable(t.a3, digits = c(1), align = 'c', "html", booktabs=T, col.names = c('Minimum', 'Lower quartile', 'Median', 'Mean', 'Upper quartile', 'Maximum'), row.names=T, caption = "Table S3: Distribution of apparent temperature sensitivities of heterotrophic soil respiration rate among 129 unique observations. Apparent temperature sensitivity was estimated as $E_{A}$ parameter ($kJ~mol^{-1}$) of two different equations (eqs. 3 and 4 in Materials and Methods section).") %>% 
  kable_styling(bootstrap_options = c("hover")) 

```

Both equations fit the data with different goodness. The goodness of fit for each observation is compared in following figure. 

```{r echo=FALSE, fig.height=4, fig.width=6, message=FALSE, warning=FALSE, fig.cap="Fig. S5: Coefficients of determination (R2) of the fits of equations 3 and 4 (see Materials and Methods for details) for individual observations (n=129). Solid black line denotes 1:1 correspondence. When the symbol is below the 1:1 line, first order decay equation fit the data better than multiplicative equation and vice versa."}

r2<-dat.results
r2$Legend<-ifelse(dat.results$R2s>dat.results$R2sb, "a", "b")
ggplot(r2, aes(R2s, R2sb))+geom_point(size=2,shape=21, alpha=0.5,aes(fill=Legend), show.legend = F)+
  geom_abline(intercept = 0, slope = 1, colour="black", lwd=0.5)+
  xlab(expression(paste(R^{2}, " - First order")))+
  ylab(expression(paste(R^{2}, " - Multiplicative")))+
  scale_fill_manual(values = c("indianred3", "dodgerblue3"))+
  theme_bw()+xlim(0,1)+ylim(0,1)+
  theme(axis.line.x = element_blank(),
        axis.line.y =element_blank(),
        plot.background=element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.text.y = element_text(size=12,colour="black"),
        axis.text.x = element_text(size=12,colour="black"),
        axis.title = element_text(size=12,colour="black"),
        legend.text=element_text(size=10,colour="black"),
        legend.title=element_blank(),
        legend.justification=c(1,0), legend.position=c(0.99,0.01),
        legend.key.size = unit(1,'lines'),
        legend.background=element_rect(fill=NA, colour=NA),
        strip.text.x = element_text(size=10),
        strip.background = element_rect(colour="black", fill = "white"),
        panel.spacing = unit(0.5, "lines"))
```

Next, observations are divided into three categories defining direction of temperature-associated change of soil microbial biomass - "Increasing", "Decreasing", "Constant". Relationship between microbial biomass and temperature is fitted as a linearized form of Arrhenius equation. 
Categories are defined based on the estimated $E_{A}$ parameter. When the 95% confidence interval of the $E_{A}$ parameter is negative, microbial biomass is considered increasing with temperature. In opposite case, microbial biomass is considered decreasing with temperature. When the 95% confidence interval includes zero, microbial biomass is considered constant.
Observation 31 - 34 are treated separately, because microbial biomass increases with temperature first and then decreases with the temperature. Results are visualized.

```{r Biomass plot, echo=FALSE, fig.height=35, fig.width=10, fig.cap="Fig. S6: Relationship between the microbial biomass carbon and temperature. Solid lines represent fit of linearized Arrhenius equation. Red symbols and lines denote decreasing trend of microbial biomass with temperature, green symbols and lines represent increasing trend and grey symbols and lines denote no or inconsistent relationship between the temperature and microbial biomass carbon (thus defined as "Constant"). ", message=FALSE, warning=FALSE}
b_change<-function(data){
  
  #list of unique observations
  IDs<-unique(data$ID)
  
  #defining all variables to calculate
  #parameters
  logkmic<-numeric()
  Ea.mic<-numeric()
  
  #standard errors
  Ea.mic.l<-numeric()
  Ea.mic.u<-numeric()
  
  #creating function for parameters estimation
  estim<-function(fr){
  
    Temp<-1/8.314/as.numeric(fr[, "Temperature"])
    obs<-log(as.numeric(fr[, "Biomass"]))
      
    lm1<-lm(obs~Temp)
    
    #best parameters
    p<-coef(lm1)
    
    
    #sd of parameters
    p.sd<-confint(lm1)[c(2,4)]
    
    #return list with opt_par and par_prof
    estim_out<-list()
    estim_out$pars<-p
    estim_out$pars.sd<-p.sd
    
    
    return(estim_out)
  }
  
  #do the calculation
  for(i in IDs){
    
    res<-estim(fr=data[data$ID==i, ])
    
    logkmic<-append(logkmic, rep(as.numeric(res$pars[1]), times=nrow(data[data$ID==i, ])))
    Ea.mic<-append(Ea.mic, rep(as.numeric(res$pars[2]), times=nrow(data[data$ID==i, ])))
    Ea.mic.l<-append(Ea.mic.l, rep(as.numeric(res$pars.sd[1]), times=nrow(data[data$ID==i, ])))
    Ea.mic.u<-append(Ea.mic.u, rep(as.numeric(res$pars.sd[2]), times=nrow(data[data$ID==i, ])))
    
    
  }
  
  Category<-character()
  
  for(i in 1:length(Ea.mic)){
      if(Ea.mic[i]<0 & Ea.mic.u[i]<0){#
        Category<-append(Category, "Increasing")
      }else{
        if(Ea.mic[i]>0 & Ea.mic.l[i]>0){#
          Category<-append(Category, "Decreasing")
        }else{
          Category<-append(Category, "Constant")
        }
      }
    }
  
  
  return(data.frame(logkmic, Ea.mic, Category))
  
}

dat.results2<-cbind(dat.results, b_change(dat))

#31
lm31<-lm(log(Biomass)~Temp, dat.results2[dat.results2$ID==31, ])
lm31o<-segmented(lm31, seg.Z = ~Temp)



dat.results2[dat.results2$ID==31, "Category"]<-ifelse(dat.results2[dat.results2$ID==31, "Temp"]>=lm31o$psi[2], "Increasing", "Decreasing")

dat.results2[(dat.results2$ID==31 & dat.results2$Category=="Increasing"),
             c("logkmic", "Ea.mic")]<-
  b_change(dat.results2[(dat.results2$ID==31 & dat.results2$Category=="Increasing"), ])[, c(1,2)]

dat.results2[(dat.results2$ID==31 & dat.results2$Category=="Decreasing"),
             c("logkmic", "Ea.mic")]<-
  b_change(dat.results2[(dat.results2$ID==31 & dat.results2$Category=="Decreasing"), ])[, c(1,2)]

dat.results2[(dat.results2$ID==31 & dat.results2$Category=="Increasing"),
             c("logks", "Eas", "logks.sd", "Eas.sd", "R2s", "AICs", "lls")]<-
  first_order(dat.results2[(dat.results2$ID==31 & dat.results2$Category=="Increasing"), ])


dat.results2[(dat.results2$ID==31 & dat.results2$Category=="Decreasing"),
             c("logks", "Eas", "logks.sd", "Eas.sd", "R2s", "AICs", "lls")]<-
  first_order(dat.results2[(dat.results2$ID==31 & dat.results2$Category=="Decreasing"), ])

dat.results2[(dat.results2$ID==31 & dat.results2$Category=="Increasing"),
             c("logksb", "Easb", "logksb.sd", "Easb.sd", "R2sb", "AICsb", "llsb")]<-
  coupled(dat.results2[(dat.results2$ID==31 & dat.results2$Category=="Increasing"), ])


dat.results2[(dat.results2$ID==31 & dat.results2$Category=="Decreasing"),
             c("logksb", "Easb", "logksb.sd", "Easb.sd", "R2sb", "AICsb", "llsb")]<-
  coupled(dat.results2[(dat.results2$ID==31 & dat.results2$Category=="Decreasing"), ])

#32
lm32<-lm(log(Biomass)~Temp, dat.results2[dat.results2$ID==32, ])
lm32o<-segmented(lm32, seg.Z = ~Temp)



dat.results2[dat.results2$ID==32, "Category"]<-ifelse(dat.results2[dat.results2$ID==32, "Temp"]>=lm32o$psi[2], "Constant", "Decreasing")

dat.results2[(dat.results2$ID==32 & dat.results2$Category=="Constant"),
             c("logkmic", "Ea.mic")]<-
  b_change(dat.results2[(dat.results2$ID==32 & dat.results2$Category=="Constant"), ])[, c(1,2)]

dat.results2[(dat.results2$ID==32 & dat.results2$Category=="Decreasing"),
             c("logkmic", "Ea.mic")]<-
  b_change(dat.results2[(dat.results2$ID==32 & dat.results2$Category=="Decreasing"), ])[, c(1,2)]

dat.results2[(dat.results2$ID==32 & dat.results2$Category=="Constant"),
             c("logks", "Eas", "logks.sd", "Eas.sd", "R2s", "AICs", "lls")]<-
  first_order(dat.results2[(dat.results2$ID==32 & dat.results2$Category=="Constant"), ])


dat.results2[(dat.results2$ID==32 & dat.results2$Category=="Decreasing"),
             c("logks", "Eas", "logks.sd", "Eas.sd", "R2s", "AICs", "lls")]<-
  first_order(dat.results2[(dat.results2$ID==32 & dat.results2$Category=="Decreasing"), ])

dat.results2[(dat.results2$ID==32 & dat.results2$Category=="Constant"),
             c("logksb", "Easb", "logksb.sd", "Easb.sd", "R2sb", "AICsb", "llsb")]<-
  coupled(dat.results2[(dat.results2$ID==32 & dat.results2$Category=="Constant"), ])


dat.results2[(dat.results2$ID==32 & dat.results2$Category=="Decreasing"),
             c("logksb", "Easb", "logksb.sd", "Easb.sd", "R2sb", "AICsb", "llsb")]<-
  coupled(dat.results2[(dat.results2$ID==32 & dat.results2$Category=="Decreasing"), ])

#33
lm33<-lm(log(Biomass)~Temp, dat.results2[dat.results2$ID==33, ])
lm33o<-segmented(lm33, seg.Z = ~Temp)



dat.results2[dat.results2$ID==33, "Category"]<-ifelse(dat.results2[dat.results2$ID==33, "Temp"]>=lm33o$psi[2], "Increasing", "Decreasing")

dat.results2[(dat.results2$ID==33 & dat.results2$Category=="Increasing"),
             c("logkmic", "Ea.mic")]<-
  b_change(dat.results2[(dat.results2$ID==33 & dat.results2$Category=="Increasing"), ])[, c(1,2)]

dat.results2[(dat.results2$ID==33 & dat.results2$Category=="Decreasing"),
             c("logkmic", "Ea.mic")]<-
  b_change(dat.results2[(dat.results2$ID==33 & dat.results2$Category=="Decreasing"), ])[, c(1,2)]

dat.results2[(dat.results2$ID==33 & dat.results2$Category=="Increasing"),
             c("logks", "Eas", "logks.sd", "Eas.sd", "R2s", "AICs", "lls")]<-
  first_order(dat.results2[(dat.results2$ID==33 & dat.results2$Category=="Increasing"), ])


dat.results2[(dat.results2$ID==33 & dat.results2$Category=="Decreasing"),
             c("logks", "Eas", "logks.sd", "Eas.sd", "R2s", "AICs", "lls")]<-
  first_order(dat.results2[(dat.results2$ID==33 & dat.results2$Category=="Decreasing"), ])

dat.results2[(dat.results2$ID==33 & dat.results2$Category=="Increasing"),
             c("logksb", "Easb", "logksb.sd", "Easb.sd", "R2sb", "AICsb", "llsb")]<-
  coupled(dat.results2[(dat.results2$ID==33 & dat.results2$Category=="Increasing"), ])


dat.results2[(dat.results2$ID==33 & dat.results2$Category=="Decreasing"),
             c("logksb", "Easb", "logksb.sd", "Easb.sd", "R2sb", "AICsb", "llsb")]<-
  coupled(dat.results2[(dat.results2$ID==33 & dat.results2$Category=="Decreasing"), ])

#34
lm34<-lm(log(Biomass)~Temp, dat.results2[dat.results2$ID==34, ])
lm34o<-segmented(lm34, seg.Z = ~Temp)



dat.results2[dat.results2$ID==34, "Category"]<-ifelse(dat.results2[dat.results2$ID==34, "Temp"]>0.0004102986, "Increasing", "Decreasing")

dat.results2[(dat.results2$ID==34 & dat.results2$Category=="Increasing"),
             c("logkmic", "Ea.mic")]<-
  b_change(dat.results2[(dat.results2$ID==34 & dat.results2$Category=="Increasing"), ])[, c(1,2)]

dat.results2[(dat.results2$ID==34 & dat.results2$Category=="Decreasing"),
             c("logkmic", "Ea.mic")]<-
  b_change(dat.results2[(dat.results2$ID==34 & dat.results2$Category=="Decreasing"), ])[, c(1,2)]

dat.results2[(dat.results2$ID==34 & dat.results2$Category=="Increasing"),
             c("logks", "Eas", "logks.sd", "Eas.sd", "R2s", "AICs", "lls")]<-
  first_order(dat.results2[(dat.results2$ID==34 & dat.results2$Category=="Increasing"), ])


dat.results2[(dat.results2$ID==34 & dat.results2$Category=="Decreasing"),
             c("logks", "Eas", "logks.sd", "Eas.sd", "R2s", "AICs", "lls")]<-
  first_order(dat.results2[(dat.results2$ID==34 & dat.results2$Category=="Decreasing"), ])

dat.results2[(dat.results2$ID==34 & dat.results2$Category=="Increasing"),
             c("logksb", "Easb", "logksb.sd", "Easb.sd", "R2sb", "AICsb", "llsb")]<-
  coupled(dat.results2[(dat.results2$ID==34 & dat.results2$Category=="Increasing"), ])


dat.results2[(dat.results2$ID==34 & dat.results2$Category=="Decreasing"),
             c("logksb", "Easb", "logksb.sd", "Easb.sd", "R2sb", "AICsb", "llsb")]<-
  coupled(dat.results2[(dat.results2$ID==34 & dat.results2$Category=="Decreasing"), ])


ggplot(dat.results2, aes(Temperature-273.15, Biomass))+
  geom_point(size=2,shape=21, alpha=0.5, aes(fill=Category))+
  geom_line(data=dat.results2, aes(Temperature-273.15, exp(logkmic)*exp(Ea.mic/Temperature/8.314), colour=Category))+
  facet_wrap(~ID, scales="free", ncol = 6)+xlab("Temperature (°C)")+
  scale_fill_manual(values = c("grey60", "brown1", "seagreen3"))+
  scale_colour_manual(values = c("grey60", "brown1", "seagreen3"))+
  ylab(expression(paste("Microbial biomass ( ",mu, "mol ",g^{-1}, ")")))+theme_bw()+
  theme(axis.line.x = element_blank(),
        axis.line.y =element_blank(),
        plot.background=element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.text.y = element_text(size=10,colour="black"),
        axis.text.x = element_text(size=10,colour="black"),
        axis.title = element_text(size=10,colour="black"),
        legend.text=element_text(size=10,colour="black"),
        legend.title=element_blank(),
        legend.justification=c(1,0), legend.position=c(0.99,0.01),
        legend.key.size = unit(1,'lines'),
        legend.background=element_rect(fill=NA, colour=NA),
        strip.text.x = element_text(size=10),
        strip.background = element_rect(colour="black", fill = "white"),
        panel.spacing = unit(0.5, "lines"))



```

Effect of defined categories on temperature sensitivity of $R_{SOIL}$ is analyzed by generalized linear regression. Every $E_{A}$ estimate is weighted by its inverse normal distribution variance. Pairwise comparison between categories is done by TukeyHSD test. Results are visualized. 

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Fig. S7: Temperature sensitivities of three different categories defining the observed trend of the microbial biomass change along the increasing temperature (Decreasing, Constant, Increasing). Temperature sensitivity was estimated as an activation energy parameter ($E_{A}$) of eq. 3 (A) and 4 (B). Grey points represent individual $E_{A}$ estimates (estimated for each observation separately). Grey error bars represent the standard deviation of the estimate. Blue points represent the mean $E_{A}$ estimated for each category by generalized linear regression. Corresponding error bars determine 95% confidence intervals of the estimate. Letters above the symbols summarize results of TukeyHSD post hoc pairwise comparison between categories. Temperature sensitivities of all categories expressed as a $Q_{10}$ parameter (in temperature interval 10 - 20 °C) are reported below the symbols."}
ea_boxplot<-dat.results2[!duplicated(dat.results2$Eas),]
lm.categories<-lm(Eas~Category, weights = 1/Eas.sd^2, 
                  ea_boxplot)

# summary(lm.categories)
# anova(lm.categories)
# emmeans(lm.categories, pairwise~Category)

# coef(lm.categories)
# exp(coef(lm.categories)[1]/8.314*(1/293.15-1/283.15))

lbd<-paste("Q[10] == ",round(exp((coef(lm.categories)[1]+coef(lm.categories)[2])/8.314*(1/293.15-1/283.15)), 1))
lbc<-paste("Q[10] == ",round(exp(coef(lm.categories)[1]/8.314*(1/293.15-1/283.15)), 1))
lbi<-paste("Q[10] == ",round(exp((coef(lm.categories)[1]+coef(lm.categories)[3])/8.314*(1/293.15-1/283.15)), 1))

ea_boxplot$Category<-factor(ea_boxplot$Category, levels = c("Decreasing", "Constant", "Increasing"))
ea_stat<-data.frame(Eas=c(coef(lm.categories)[1],
                            coef(lm.categories)[1]+coef(lm.categories)[2],
                            coef(lm.categories)[1]+coef(lm.categories)[3]),
                     Eas.l=c(confint(lm.categories)[1,1],
                              coef(lm.categories)[1]+confint(lm.categories, level = 0.99)[2,1],
                              coef(lm.categories)[1]+confint(lm.categories, level = 0.99)[3,1]),
                     Eas.u=c(confint(lm.categories)[1,2],
                              coef(lm.categories)[1]+confint(lm.categories, level = 0.99)[2,2],
                              coef(lm.categories)[1]+confint(lm.categories, level = 0.99)[3,2]),
                     Category=c("Constant", "Decreasing", "Increasing"))

#6 to 6 inches when exported to pdf
ea1<-ggplot(ea_boxplot, aes(Category, Eas/1000))+
  geom_pointrange(aes(ymin=Eas/1000-Eas.sd/1000, ymax=Eas/1000+Eas.sd/1000),position = position_jitter(width = 0.33),size=0.5, fill="grey60", shape=21,alpha=0.4)+
  #stat_summary(size = 1,fun.y = "median",fun.ymin = min, fun.ymax = max,fill="dodgerblue3", shape=21)+
  geom_point(data=ea_stat, size=6, fill="dodgerblue3", shape=21, aes(Category, Eas/1000))+
  geom_errorbar(data=ea_stat, aes(ymin=Eas.l/1000, ymax=Eas.u/1000), lwd=1, width=0.01)+
  ylab(expression(paste(italic(E[A])~(kJ~mol^{-1}))))+
  theme_bw()+scale_y_continuous(limits = c(-310,150), expand = c(0, 0))+
  theme(axis.line.x = element_blank(),
        axis.line.y =element_blank(),
        plot.background=element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.text.y = element_text(size=14,colour="black"),
        axis.text.x = element_text(size=14,colour="black"),
        axis.title = element_text(size=14,colour="black"),
        axis.title.x = element_blank(),
        legend.text=element_text(size=10,colour="black"),
        legend.title=element_blank(),
        legend.justification=c(1,0), legend.position=c(0.99,0.01),
        legend.key.size = unit(1,'lines'),
        legend.background=element_rect(fill=NA, colour=NA),
        strip.text.x = element_text(size=10),
        strip.background = element_rect(colour="black", fill = "white"),
        panel.spacing = unit(0.25, "lines"),
        plot.title=element_text(size=16, face="bold", hjust=-0.05))+
  annotate("text", label="a", 1, 125, size=6)+
  annotate("text", label="b", 2, 125, size=6)+
  annotate("text", label="b", 3, 125, size=6)+
  annotate("text", label=lbd, 1, y=c(-290), size=4.5, parse=T)+
  annotate("text", label=lbc, 2, y=c(-290), size=4.5, parse=T)+
  annotate("text", label=lbi, 3, y=c(-290), size=4.5, parse=T)+
  ggtitle("A)")


lm.categories2<-lm(Easb~Category, weights = 1/Easb.sd^2, 
                  ea_boxplot)

# summary(lm.categories2)
# anova(lm.categories2)
# emmeans(lm.categories2, pairwise~Category)
# 
# coef(lm.categories2)
# exp(coef(lm.categories2)[1]/8.314*(1/293.15-1/283.15))

lbc2<-paste("Q[10] == ",round(exp((coef(lm.categories2)[1]+coef(lm.categories2)[2])/8.314*(1/293.15-1/283.15)), 1))
lbd2<-paste("Q[10] == ",round(exp(coef(lm.categories2)[1]/8.314*(1/293.15-1/283.15)), 1))
lbi2<-paste("Q[10] == ",round(exp((coef(lm.categories2)[1]+coef(lm.categories2)[3])/8.314*(1/293.15-1/283.15)), 1))

ea_boxplot$Category<-factor(ea_boxplot$Category, levels = c("Decreasing", "Constant", "Increasing"))
ea_stat2<-data.frame(Easb=c(coef(lm.categories2)[1],
                     coef(lm.categories2)[1]+coef(lm.categories2)[2],
                     coef(lm.categories2)[1]+coef(lm.categories2)[3]),
                     Easb.l=c(confint(lm.categories2)[1,1],
                                coef(lm.categories2)[1]+confint(lm.categories2, level=0.99)[2,1],
                                coef(lm.categories2)[1]+confint(lm.categories2, level=0.99)[3,1]),
                     Easb.u=c(confint(lm.categories2)[1,2],
                              coef(lm.categories2)[1]+confint(lm.categories2, level=0.99)[2,2],
                              coef(lm.categories2)[1]+confint(lm.categories2, level=0.99)[3,2]),
                     Category=c("Decreasing", "Constant", "Increasing"))

ea2<-ggplot(ea_boxplot, aes(Category, Easb/1000))+
  geom_pointrange(aes(ymin=Easb/1000-Easb.sd/1000, ymax=Easb/1000+Easb.sd/1000),position = position_jitter(width = 0.33),size=0.5, fill="grey60", shape=21,alpha=0.4)+
  #stat_pointrange(size = 1,aes(y),fill="dodgerblue3", shape=21)+
  geom_point(data=ea_stat2, size=6, fill="dodgerblue3", shape=21, aes(Category, Easb/1000))+
  geom_errorbar(data=ea_stat2, aes(ymin=Easb.l/1000, ymax=Easb.u/1000), lwd=1, width=0.01)+
  ylab(expression(paste(italic(E[A])~(kJ~mol^{-1}))))+
  theme_bw()+scale_y_continuous(limits = c(-310,150), expand = c(0, 0))+
  theme(axis.line.x = element_blank(),
        axis.line.y =element_blank(),
        plot.background=element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.text.y = element_blank(),
        axis.text.x = element_text(size=14,colour="black"),
        axis.title = element_text(size=14,colour="black"),
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        legend.text=element_text(size=10,colour="black"),
        legend.title=element_blank(),
        legend.justification=c(1,0), legend.position=c(0.99,0.01),
        legend.key.size = unit(1,'lines'),
        legend.background=element_rect(fill=NA, colour=NA),
        strip.text.x = element_text(size=10),
        strip.background = element_rect(colour="black", fill = "white"),
        panel.spacing = unit(0.25, "lines"),
        plot.title=element_text(size=16, face="bold", hjust=-0.05),
        plot.margin=unit(c(0.075, 0.8, 0.075, 0.075), "in"))+
  annotate("text", label="a", 1, 125, size=6)+
  annotate("text", label="a", 2, 125, size=6)+
  annotate("text", label="a", 3, 125, size=6)+
  annotate("text", label=lbd2, 1, y=c(-290), size=4.5, parse=T)+
  annotate("text", label=lbc2, 2, y=c( -290), size=4.5, parse=T)+
  annotate("text", label=lbi2, 3, y=c(-290), size=4.5, parse=T)+
  ggtitle("B)")

grid.arrange(ea1, ea2, ncol=2)

```

##Supplementary analyses
Across all observations, 15 different equations were fitted and their goodness of fit was compared by AIC. Following equations were used:

[1] $R_{SOIL}~=~\alpha~+~\beta~\times~C_{S}$

[2] $R_{SOIL}~=~\alpha~+~\beta~\times~C_{MB}$

[3] $R_{SOIL}~=~k~\times~C_{S}~\times~C_{MB}$

[4] $R_{SOIL}~=~V_{MAX}~\times~C_{S}~\times~C_{MB}~\times~\frac{1}{K_{M}~+~C_{S}}$

[5] $R_{SOIL}~=~V_{MAX}~\times~DOC~\times~C_{MB}~\times~\frac{1}{K_{M}~+DOC}$

[6] $R_{SOIL}~=~V_{MAX}~\times~C_{S}~\times~C_{MB}~\times~\frac{1}{K_{M}~+C_{S}}~\times~(1~-~CUE)$

where 

$CUE~=~\emptyset~\times~(\frac{N:C_{S}}{N:C_{MB}})^{\tau}$

[7] $R_{SOIL}~=~A~\times~e^{\frac{E_{A}}{R~\times~T}}$

[8] $R_{SOIL}~=~k~\times~C_{S}~\times~e^{\frac{E_{A}}{R~\times~T}}$

[9] $R_{SOIL}~=~k~\times~C_{S}~\times~C_{MB}~\times~e^{\frac{E_{A}}{R~\times~T}}$

[10] $R_{SOIL}~=~C_{S}~\times~C_{MB}~\times~V^{0}_{MAX}~\times~e^{\frac{E_{A-V_{MAX}}}{R~\times~T}}~\times~\frac{1}{K_{M}~+~C_{S}}$

[11] $R_{SOIL}~=~DOC~\times~C_{MB}~\times~V^{0}_{MAX}~\times~e^{\frac{E_{A-V_{MAX}}}{R~\times~T}}~\times~\frac{1}{K_{M}~+~DOC}$

[12] $R_{SOIL}~=~C_{S}~\times~C_{MB}~\times~V^{0}_{MAX}~\times~e^{\frac{E_{A-V_{MAX}}}{R~\times~T}}~\times~\frac{1}{K^{0}_{M}~\times~e^{\frac{E_{A-K_{M}}}{R~\times~T}}~+~C_{S}}$

[13] $R_{SOIL}~=~DOC~\times~C_{MB}~\times~V^{0}_{MAX}~\times~e^{\frac{E_{A-V_{MAX}}}{R~\times~T}}~\times~\frac{1}{K^{0}_{M}~\times~e^{\frac{E_{A-K_{M}}}{R~\times~T}}~+~DOC}$

[14] $R_{SOIL}~=~C_{S}~\times~C_{MB}~\times~V^{0}_{MAX}~\times~e^{\frac{E_{A-V_{MAX}}}{R~\times~T}}~\times~\frac{1}{K^{0}_{M}~\times~e^{\frac{E_{A-K_{M}}}{R~\times~T}}~+~C_{S}}~\times~[1~-~CUE_{0}~-~\omega~(T~-~273.15)]$

[15] $R_{SOIL}~=~DOC~\times~C_{MB}~\times~V^{0}_{MAX}~\times~e^{\frac{E_{A-V_{MAX}}}{R~\times~T}}~\times~\frac{1}{K^{0}_{M}~\times~e^{\frac{E_{A-K_{M}}}{R~\times~T}}~+~DOC}~\times~[1~-~CUE_{0}~-~\omega~(T~-~273.15)]$

Symbols used in all equations are explained in Supplemntary Table 1.

```{r}
source("./Global_Eqs/ctot_global.R")
eq1<-ctot_global(dat)
source("./Global_Eqs/cmic_global.R")
eq2<-cmic_global(dat)
source("./Global_Eqs/simple_global.R")
eq3<-simple_global(dat)
source("./Global_Eqs/monod_global1.R")
eq4<-monod_global1(dat)
source("./Global_Eqs/monod_global2.R")
eq5<-monod_global2(dat[!is.na(dat$DOC), ])
source("./Global_Eqs/monod2_global.R")
eq6<-monod2_global(dat[!is.na(dat$CNs), ])
source("./Global_Eqs/nic_global.R")
eq7<-nic_global(dat)
source("./Global_Eqs/first_global.R")
eq8<-first_global(dat)
source("./Global_Eqs/coupled_global.R")
eq9<-coupled_global(dat)
source("./Global_Eqs/monod_Vmax.R")
eq10<-monod_Vmax(dat)
source("./Global_Eqs/monod_Vmax2.R")
eq11<-monod_Vmax2(dat[!is.na(dat$DOC), ])
source("./Global_Eqs/monod_VmaxKm.R")
eq12<-monod_VmaxKm(dat)
source("./Global_Eqs/monod_VmaxKm2.R")
eq13<-monod_VmaxKm2(dat[!is.na(dat$DOC), ])
source("./Global_Eqs/monod_VmaxKmCUE.R")
eq14<-monod_VmaxKmCUE(dat)
source("./Global_Eqs/monod_VmaxKmCUE2.R")
eq15<-monod_VmaxKmCUE2(dat[!is.na(dat$DOC), ])

```


```{r}
cor1<-dat[,c(2,4,6, 7, 9, 11, 13, 16, 22)]
cor1[,c(4, 5, 6, 7)]<-log(cor1[,c(4, 5, 6, 7)])
chart.Correlation(cor1, histogram = T, pch=19)

```

```{r}


cor2<-ea_boxplot[,c(4, 6, 10, 14, 16, 22, 25, 39)]
chart.Correlation(cor2, histogram = T, pch=19)

ggplot(dat.results2[dat.results2$Ea.mic<400000, ], aes((Eas-Easb)/1000, Ea.mic/1000))+geom_point()



```